\subsection{Devotions from Os Hillman}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{The Skillfull Worker}

\index[speaker]{Os Hillman!Proverb 22:29 (The Skillfull Worker)}
\index[series]{Proverbs (Os Hillman)!Pro  22:29 (The Skillfull Worker}
\index[date]{2021/12/21!Proverb  22:29 (The Skillfull Worker) (Os Hillman)}

\index[DEVOTIONAL]{TGIF1!Os Hillman (The Skillfull Worker) - Proverb  22:29!2022/01/21}

\noindent The Lord has called each of us to be excellent in what we do. Those whom God used in the Kingdom as workplace ministers were skilled and exemplified excellence in their field. Not only were these men skilled, they were filled with God's Spirit.\\
\\
\noindent Then the Lord said to Moses, "See, I have chosen Bezalel son of Uri, the son of Hur, of the tribe of Judah, and I have filled him with the Spirit of God, with skill, ability and knowledge in all kinds of crafts - to make artistic designs for work in gold, silver and bronze, to cut and set stones, to work in wood, and to engage in all kinds of craftsmanship" (Exodus 31:1-5).\\
\\
\noindent Consider Huram, the master craftsman of bronze in whom Solomon entrusted much of the temple designs. He was a true master craftsman (see 1 Kings 7:14).\\
\\
\noindent Consider Joseph, whose skill as an administrator was known throughout Egypt and the world. Consider Daniel, who served his king with great skill and integrity. The list could go on - David, Nehemiah, Acquilla and Priscilla.\\
\\
\noindent I recall the first issue of an international publication we began. It was common to hear the comment, "It doesn't even look like a Christian magazine." They were saying the quality and excellence exceeded what they equated to Christian work. What a shame. Has inferior quality become synonymous with Christian work?\\
\\
May we strive for excellence in all that we do for the Master of the universe.\\
\\
\noindent Whatever you do, work at it with all your heart, as working for the Lord, not for men, since you know that you will receive an inheritance from the Lord as a reward. It is the Lord Christ you are serving (Colossians 3:23-24).


