\chapter{Hebrews 9}\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{THE PERFECT PRIEST}}\\ (Hebrews 9:9-28) \begin{compactenum}[I.][8]
    \item Law was a way not yet \textbf{Perfect} \index[scripture]{Hebrews!Hebrews 09:09}\index[scripture]{Hebrews!Hebrews 09:11} (Hebrews 9:9, 11)
    \item Law allowed only Temporary \textbf{Purification} of God \index[scripture]{Hebrews!Hebrews 09:13} (Hebrews 9:13)
    \item But now can have a \textbf{Purged} conscience \index[scripture]{Hebrews!Hebrews 09:14} (Hebrews 9:14)
    \item Old way was the \textbf{Precepts} of Moses \index[scripture]{Hebrews!Hebrews 09:19} (Hebrews 9:19)
    \item Old way showed  \textbf{Patterns} of the real way \index[scripture]{Hebrews!Hebrews 09:23} (Hebrews 9:23)
    \item Into the \textbf{Presence} of God \index[scripture]{Hebrews!Hebrews 09:24} (Hebrews 9:24)
\end{compactenum}}

% \textcolor[cmyk]{0.99998,1,0,0}{
% \footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://www.audioverse.org/english/audiobibles/books/ENGKJV/N/Heb/1}{\textcolor[cmyk]{0.99998,1,0,0}{Hebrews Audio}}}

\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://www.audioverse.org/english/audiobibles/books/ENGKJV/N/Heb/1}{\textcolor[cmyk]{0.99998,1,0,0}{Hebrews Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{Then verily the first \emph{covenant} had also ordinances of divine service, and a worldly sanctuary.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{For there was a tabernacle made; the first, wherein \emph{was} the candlestick, and the table, and the shewbread; which is called the sanctuary.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{And after the second veil, the tabernacle which is called the Holiest of all;}
[4] \textcolor[cmyk]{0.99998,1,0,0}{Which had the golden censer, and the ark of the covenant overlaid round about with gold, wherein \emph{was} the golden pot that had manna, and Aaron's rod that budded, and the tables of the covenant;}\footnote{\textbf{Numbers 4:14} - And they shall put upon it all the vessels thereof, wherewith they minister about it, even the censers, the fleshhooks, and the shovels, and the basons, all the vessels of the altar; and they shall spread upon it a covering of badgers’ skins, and put to the staves of it.}\footnote{\textbf{Numbers 14:46-47} - And Moses said unto Aaron, Take a censer, and put fire therein from off the altar, and put on incense, and go quickly unto the congregation, and make an atonement for them: for there is wrath gone out from the LORD; the plague is begun. [47] And Aaron took as Moses commanded, and ran into the midst of the congregation; and, behold, the plague was begun among the people: and he put on incense, and made an atonement for the people.}\footnote{\textbf{Numbers 17:8} - And it came to pass, that on the morrow Moses went into the tabernacle of witness; and, behold, the rod of Aaron for the house of Levi was budded, and brought forth buds, and bloomed blossoms, and yielded almonds.}\footnote{\textbf{2 Chronicles 26:18-19} - And they withstood Uzziah the king, and said unto him, It appertaineth not unto thee, Uzziah, to burn incense unto the LORD, but to the priests the sons of Aaron, that are consecrated to burn incense: go out of the sanctuary; for thou hast trespassed; neither shall it be for thine honour from the LORD God. [19] Then Uzziah was wroth, and had a censer in his hand to burn incense: and while he was wroth with the priests, the leprosy even rose up in his forehead before the priests in the house of the LORD, from beside the incense altar.}\footnote{\textbf{Leviticus 16:12-13} - And he shall take a censer full of burning coals of fire from off the altar before the LORD, and his hands full of sweet incense beaten small, and bring it within the vail: [13] And he shall put the incense upon the fire before the LORD, that the cloud of the incense may cover the mercy seat that is upon the testimony, that he die not:}\footnote{\textbf{Revelation 8:3-5} - And another angel came and stood at the altar, having a golden censer; and there was given unto him much incense, that he should offer it with the prayers of all saints upon the golden altar which was before the throne. [4] And the smoke of the incense, which came with the prayers of the saints, ascended up before God out of the angel’s hand. [5] And the angel took the censer, and filled it with fire of the altar, and cast it into the earth: and there were voices, and thunderings, and lightnings, and an earthquake.} 
[5] \textcolor[cmyk]{0.99998,1,0,0}{And over it the cherubims of glory shadowing the mercyseat; of which we cannot now speak particularly.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{Now when these things were thus ordained, the priests went always into the first tabernacle, \fcolorbox{bone}{MYGOLD}{accomplishing} the service \emph{of} \emph{God}.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{But into the second \emph{went} the high priest alone once every year, not without blood, which he offered for himself, and \emph{for} the errors of the people:}
[8] \textcolor[cmyk]{0.99998,1,0,0}{The Holy Ghost this signifying, that the way into the holiest of all was not yet made manifest, while as the first tabernacle was yet standing:}
[9] \textcolor[cmyk]{0.99998,1,0,0}{Which \emph{was} a figure for the time then present, in which were offered both gifts and sacrifices, that could not make him that did the service perfect, as pertaining to the conscience;}
[10] \textcolor[cmyk]{0.99998,1,0,0}{\emph{Which} \emph{stood} only in meats and drinks, and divers washings, and carnal ordinances, imposed \emph{on} \emph{them} until the time of reformation.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{But Christ being come an high priest of good things to come, by a greater and more \fcolorbox{bone}{lime}{perfect} tabernacle, not made with hands, that is to say, not of this building;}
[12] \textcolor[cmyk]{0.99998,1,0,0}{Neither by the blood of goats and calves, but by his own blood he entered in once into the holy place, having obtained eternal redemption \emph{for} \emph{us}.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{For if the blood of bulls and of goats, and the ashes of an heifer sprinkling the unclean, sanctifieth to the \fcolorbox{bone}{lime}{purifying} of the flesh:}
[14] \textcolor[cmyk]{0.99998,1,0,0}{How much more shall the blood of Christ, who through the eternal Spirit offered himself without spot to God, \fcolorbox{bone}{lime}{purge} your conscience from dead works to serve the living God?}
[15] \textcolor[cmyk]{0.99998,1,0,0}{And for this cause he is the mediator of the new testament, that by means of death, for the redemption of the transgressions \emph{that} \emph{were} under the first testament, they which are called might receive the promise of eternal inheritance.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{For where a testament \emph{is}, there must also of necessity be the death of the testator.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{For a testament \emph{is} of force after men are dead: otherwise it is of no strength at all while the testator liveth.}
[18] \textcolor[cmyk]{0.99998,1,0,0}{Whereupon neither the first \emph{testament} was dedicated without blood.}
[19] \textcolor[cmyk]{0.99998,1,0,0}{For when Moses had spoken every \fcolorbox{bone}{lime}{precept} to all the people according to the law, he took the blood of calves and of goats, with water, and scarlet wool, and hyssop, and sprinkled both the book, and all the people,}
[20] \textcolor[cmyk]{0.99998,1,0,0}{Saying, This \emph{is} the blood of the testament which God hath enjoined unto you.}
[21] \textcolor[cmyk]{0.99998,1,0,0}{Moreover he sprinkled with blood both the tabernacle, and all the vessels of the ministry.}
[22] \textcolor[cmyk]{0.99998,1,0,0}{And almost all things are by the law purged with blood; and without shedding of blood is no remission.}
[23] \textcolor[cmyk]{0.99998,1,0,0}{\emph{It} \emph{was} therefore necessary that the \fcolorbox{bone}{lime}{patterns} of things in the heavens should be purified with these; but the heavenly things themselves with better sacrifices than these.}
[24] \textcolor[cmyk]{0.99998,1,0,0}{For Christ is not entered into the holy places made with hands, \emph{which} \emph{are} the figures of the true; but into heaven itself, now to appear in the \fcolorbox{bone}{lime}{presence} of God for us:}
[25] \textcolor[cmyk]{0.99998,1,0,0}{Nor yet that he should offer himself often, as the high priest entereth into the holy place every year with blood of others;}
[26] \textcolor[cmyk]{0.99998,1,0,0}{For then must he often have suffered since the foundation of the world: but now once in the end of the world hath he appeared to put away sin by the sacrifice of himself.}
[27] \textcolor[cmyk]{0.99998,1,0,0}{And as it is appointed unto men once to die, but after this the judgment:}
[28] \textcolor[cmyk]{0.99998,1,0,0}{So Christ was once offered to bear the sins of many; and unto them that look for him shall he appear the second time without sin unto salvation.}\footnote{\textbf{Matthew 25:1-7} - Then shall the kingdom of heaven be likened unto ten virgins, which took their lamps, and went forth to meet the bridegroom. [2] And five of them were wise, and five were foolish. [3] They that were foolish took their lamps, and took no oil with them: [4] But the wise took oil in their vessels with their lamps. [5] While the bridegroom tarried, they all slumbered and slept. [6] And at midnight there was a cry made, Behold, the bridegroom cometh; go ye out to meet him. [7] Then all those virgins arose, and trimmed their lamps.}