\chapter{1 Samuel 2}



\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{HANNAH's HAPPINESS}}\\ (1 Samuel 2:1-11) \begin{compactenum}[I.][8]
    \item Her \textbf{Prayer}  \index[scripture]{1Samuel!1Sa 02:01}(1Sa 2:1) 
    \item Her \textbf{Proof}  \index[scripture]{1Samuel!1Sa 02:01}(1Sa 2:1)
    \item Her \textbf{Praise}  \index[scripture]{1Samuel!1Sa 02:02--02}(1Sa 2:2--3)
    \item Her \textbf{Perspective}  %\index[scripture]{1Samuel!1Sa 02:02--02}(1Sa 2:2--3)
    \item Her \textbf{Comparisons} \index[scripture]{1Samuel!1Sa 02:04--08}  (1Sa 2:4--8)
    \item Her \textbf{Prophecy}  \index[scripture]{1Samuel!1Sa 02:10}(1Sa 2:10)
    \item Her \textbf{Performance}  \index[scripture]{1Samuel!1Sa 02:11}(1Sa 2:11) -- fulfills her promise
\end{compactenum}}






\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/1_samuel_2.html}{\textcolor[cmyk]{0.99998,1,0,0}{1 Samuel 2 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{And Hannah \fcolorbox{bone}{lime}{prayed}, and said, My heart rejoiceth in the LORD, mine horn is exalted in the LORD: my mouth is \fcolorbox{bone}{lime}{enlarged} over mine enemies; because I rejoice in thy salvation.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{\emph{There} \emph{is} none holy as the LORD: for \emph{there} \emph{is} none beside thee: neither \emph{is} \emph{there} any rock like our God.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{Talk no more so exceeding proudly; let \emph{not} arrogancy come out of your mouth: for the LORD \emph{is} \fcolorbox{bone}{bone}{a} God of knowledge, and by him actions are \fcolorbox{bone}{lime}{weighed}.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{The bows of the mighty men \emph{are} broken, and they that stumbled are girded with strength.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{\emph{They} \emph{that} \emph{were} full have hired out themselves for bread; and \emph{they} \emph{that} \emph{were} hungry ceased: so that the barren hath born seven; and she that hath many children is waxed feeble.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{The LORD killeth, and maketh alive: he bringeth down to the grave, and bringeth up.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{The LORD maketh poor, and maketh rich: he bringeth low, and lifteth up.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{He raiseth up \fcolorbox{bone}{lime}{the poor} out of the dust, \emph{and} lifteth up the beggar from the dunghill, to set \emph{them} among princes, and to make them inherit the throne of glory: for the pillars of the earth \emph{are} the LORD'S, and he hath set the world upon them.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{He will keep the feet of his saints, and the wicked shall be silent in darkness; for by strength shall no man prevail.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{The adversaries of the LORD shall be broken to pieces; out of heaven shall he thunder upon them: the LORD shall judge the ends of the earth; and he shall give strength \fcolorbox{bone}{bone}{unto} his king, and \fcolorbox{bone}{lime}{exalt the horn} of his anointed.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{And Elkanah went to Ramah to his house. And \fcolorbox{bone}{lime}{the child did minister} \fcolorbox{bone}{bone}{unto} the LORD before Eli the priest.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Now the sons of Eli \emph{were} sons of Belial; they knew not the LORD.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{And the priests' custom with the people \emph{was,} \emph{that}, when any man offered sacrifice, the priest's servant came, while the flesh was in seething, with \fcolorbox{bone}{bone}{a} fleshhook of three teeth in his hand;}
[14] \textcolor[cmyk]{0.99998,1,0,0}{And he struck \emph{it} into the pan, or kettle, or caldron, or pot; all that the fleshhook brought up the priest took for himself. So they did in Shiloh \fcolorbox{bone}{bone}{unto} all the Israelites that came thither.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{Also before they burnt the fat, the priest's servant came, and said to the man that sacrificed, Give flesh to roast for the priest; for he will not have sodden flesh of thee, but raw.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{And \emph{if} any man said \fcolorbox{bone}{bone}{unto} him, Let them not fail to burn the fat presently, and \emph{then} take \emph{as} \emph{much} as thy soul desireth; then he would answer him, \emph{Nay}; but thou shalt give \emph{it} \emph{me} now: and if not, I will take \emph{it} by force.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{Wherefore the sin of the young men was very great before the LORD: for men abhorred the offering of the LORD.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{But Samuel ministered before the LORD, \emph{being} \fcolorbox{bone}{bone}{a} child, girded with \fcolorbox{bone}{bone}{a} linen ephod.}
[19] \textcolor[cmyk]{0.99998,1,0,0}{Moreover his mother made him \fcolorbox{bone}{bone}{a} little coat, and brought \emph{it} to him from year to year, when she came up with her husband to offer the yearly sacrifice.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Eli blessed Elkanah and his wife, and said, The LORD give thee seed of this woman for the loan which is lent to the LORD. And they went \fcolorbox{bone}{bone}{unto} their own home.}
[21] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD visited Hannah, so that she conceived, and bare three sons and two daughters. And the child Samuel grew before the LORD.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Now Eli was very old, and heard all that his sons did \fcolorbox{bone}{bone}{unto} all Israel; and how they lay with the women that assembled \emph{at} the door of the tabernacle of the congregation.}
[23] \textcolor[cmyk]{0.99998,1,0,0}{And he said \fcolorbox{bone}{bone}{unto} them, Why do ye such things? for I hear of your evil dealings by all this people.}
[24] \textcolor[cmyk]{0.99998,1,0,0}{Nay, my sons; for \emph{it} \emph{is} no good report that I hear: ye make the LORD'S people to transgress.}
[25] \textcolor[cmyk]{0.99998,1,0,0}{If one man sin against another, the judge shall judge him: but if \fcolorbox{bone}{bone}{a} man sin against the LORD, who shall intreat for him? Notwithstanding they hearkened not \fcolorbox{bone}{bone}{unto} the voice of their father, because the LORD would slay them.}
[26] \textcolor[cmyk]{0.99998,1,0,0}{And the child Samuel grew on, and was in favour both with the LORD, and also with men.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And there came \fcolorbox{bone}{bone}{a} man of God \fcolorbox{bone}{bone}{unto} Eli, and said \fcolorbox{bone}{bone}{unto} him, Thus saith the LORD, Did I plainly appear \fcolorbox{bone}{bone}{unto} the house of thy father, when they were in Egypt in Pharaoh's house?}
[28] \textcolor[cmyk]{0.99998,1,0,0}{And did I choose him out of all the tribes of Israel \emph{to} \emph{be} my priest, to offer upon mine altar, to burn incense, to wear an ephod before me? and did I give \fcolorbox{bone}{bone}{unto} the house of thy father all the offerings made by fire of the children of Israel?}
[29] \textcolor[cmyk]{0.99998,1,0,0}{Wherefore kick ye at my sacrifice and at mine offering, which I have commanded \emph{in} \emph{my} habitation; and honourest thy sons above me, to make yourselves fat with the chiefest of all the offerings of Israel my people?}
[30] \textcolor[cmyk]{0.99998,1,0,0}{Wherefore the LORD God of Israel saith, I said indeed \emph{that} thy house, and the house of thy father, should walk before me for ever: but now the LORD saith, Be it far from me; for them that honour me I will honour, and they that despise me shall be lightly esteemed.}
[31] \textcolor[cmyk]{0.99998,1,0,0}{Behold, the days come, that I will cut off thine arm, and the arm of thy father's house, that there shall not be an old man in thine house.}
[32] \textcolor[cmyk]{0.99998,1,0,0}{And thou shalt see an enemy \emph{in} \emph{my} habitation, in all \emph{the} \emph{wealth} which \emph{God} shall give Israel: and there shall not be an old man in thine house for ever.}
[33] \textcolor[cmyk]{0.99998,1,0,0}{And the man of thine, \emph{whom} I shall not cut off from mine altar, \emph{shall} \emph{be} to consume thine eyes, and to grieve thine heart: and all the increase of thine house shall die in the flower of their age.}
[34] \textcolor[cmyk]{0.99998,1,0,0}{And this \emph{shall} \emph{be} \fcolorbox{bone}{bone}{a} sign \fcolorbox{bone}{bone}{unto} thee, that shall come upon thy two sons, on Hophni and Phinehas; in one day they shall die both of them.}
[35] \textcolor[cmyk]{0.99998,1,0,0}{And I will raise me up \fcolorbox{bone}{bone}{a} faithful priest, \emph{that} shall do according to \emph{that} which \emph{is} in mine heart and in my mind: and I will build him \fcolorbox{bone}{bone}{a} sure house; and he shall walk before mine anointed for ever.}
[36] \textcolor[cmyk]{0.99998,1,0,0}{And it shall come to pass, \emph{that} every one that is left in thine house shall come \emph{and} crouch to him for \fcolorbox{bone}{bone}{a} piece of silver and \fcolorbox{bone}{bone}{a} morsel of bread, and shall say, Put me, I pray thee, into one of the priests' offices, that I may eat \fcolorbox{bone}{bone}{a} piece of bread.}