\chapter{1 Samuel 3}





\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{A NEW PRIEST}}\\ (1 Samuel 3:1-21) \begin{compactenum}[I.][8]
    \item The \textbf{Lamp Disregarded}  \index[scripture]{1Samuel!1Sa 03:03}\ (1Sa 3:3) 
    \item The \textbf{Lord's Revelation}  \index[scripture]{1Samuel!1Sa 03:05}\index[scripture]{1Samuel!1Sa 03:06}\index[scripture]{1Samuel!1Sa 03:06}  (1Sa 3:5, 6, 8) 
    \item The \textbf{Lack of  Restraint}  \index[scripture]{1Samuel!1Sa 03:14} (1Sa 3:14) 
    \item The \textbf{Lofty Recognition}  \index[scripture]{1Samuel!1Sa 03:17} (1Sa 3:17) 
    \item The \textbf{Loyal Response}  \index[scripture]{1Samuel!1Sa 03:18} (1Sa 3:18) 
    \item The \textbf{Looming Reality}  \index[scripture]{1Samuel!1Sa 03:18} (1Sa 3:18) 
    \item  \textbf{Labouring and Reliable}  \index[scripture]{1Samuel!1Sa 03:21} (1Sa 3:21) 
\end{compactenum}}







\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/1_samuel_3.html}{\textcolor[cmyk]{0.99998,1,0,0}{1 Samuel 3 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{And the child Samuel ministered unto the LORD before Eli. And the word of the LORD was precious in those days; \emph{there} \emph{was} no open vision.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And it came to pass at that time, when Eli \emph{was} laid down in his place, and his eyes began to wax dim, \emph{that} he could not see;}
[3] \textcolor[cmyk]{0.99998,1,0,0}{And ere the \fcolorbox{bone}{lime}{lamp of God went out} in the temple of the LORD, where the ark of God \emph{was}, and Samuel was laid down \emph{to} \emph{sleep};}
[4] \textcolor[cmyk]{0.99998,1,0,0}{That the LORD called Samuel: and he answered, Here \emph{am} I.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{And he ran unto Eli, and said, Here \emph{am} I; \fcolorbox{bone}{lime}{for thou calledst me}. And he said, I called not; lie down again. And he went and lay down.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD called yet again, Samuel. And Samuel arose and went to Eli, and said, Here \emph{am} I; for \fcolorbox{bone}{lime}{thou didst call me}. And he answered, I called not, my son; lie down again.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{Now Samuel did not yet know the LORD, neither was the word of the LORD yet revealed unto him.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD called Samuel again the third time. And he arose and went to Eli, and said, Here \emph{am} I; for \fcolorbox{bone}{lime}{thou didst call me}. And Eli perceived that the LORD had called the child.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{Therefore Eli said unto Samuel, Go, lie down: and it shall be, if he call thee, that thou shalt say, Speak, LORD; for thy servant heareth. So Samuel went and lay down in his place.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD came, and stood, and called as at other times, Samuel, Samuel. Then Samuel answered, Speak; for thy servant heareth.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And the LORD said to Samuel, Behold, I will do a thing in Israel, at which both the ears of every one that heareth it shall tingle.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{In that day I will perform against Eli all \emph{things} which I have spoken concerning his house: when I begin, I will also make an end.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{For I have told him that I will judge his house for ever for the iniquity which he knoweth; because his sons made themselves vile, and he \fcolorbox{bone}{lime}{restrained} \fcolorbox{bone}{lime}{them not}.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{And therefore I have sworn unto the house of Eli, that the iniquity of Eli's house shall not be purged with sacrifice nor offering for ever.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Samuel lay until the morning, and opened the doors of the house of the LORD. And Samuel feared to shew Eli the vision.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{Then Eli called Samuel, and said, Samuel, my son. And he answered, Here \emph{am} I.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{And he said, What \emph{is} the thing that \emph{the} \emph{LORD} hath said unto thee? I pray thee \fcolorbox{bone}{lime}{hide \emph{it} not} from me: God do so to thee, and more also, if thou hide \emph{any} thing from me of all the things that he said unto thee.}
[18] \textcolor[cmyk]{0.99998,1,0,0}{And Samuel \fcolorbox{bone}{lime}{told him every whit}, and hid nothing from him. And he said, It \emph{is} the LORD: \fcolorbox{bone}{lime}{let him do} what seemeth him good.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Samuel grew, and the LORD was with him, and did let none of his words fall to the ground.}
[20] \textcolor[cmyk]{0.99998,1,0,0}{And all Israel from Dan even to Beer-sheba knew that Samuel \emph{was} established \emph{to} \emph{be} a prophet of the LORD.}
[21] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD appeared again in Shiloh: for the LORD revealed himself to Samuel in Shiloh by the word of the LORD.}