\chapter{Psalm 79}
\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{THE MINISTRY OF THE HEATHEN}}\\ (Psalm 79:1-13) \begin{compactenum}[I.][8]
    \item They \textbf{Defile the Sacred}  \index[scripture]{Psalms!Psa 079:01}(Psa 79:1)
    \item They bring \textbf{Death to the Saints}  \index[scripture]{Psalms!Psa 079:02}(Psa 79:2)
    \item They use \textbf{Derision \& Scorn} \index[scripture]{Psalms!Psa 079:04}(Psa 79:4)
    \item They make \textbf{Dwellings Soiled} \index[scripture]{Psalms!Psa 079:07}(Psa 79:7)
    \item They \textbf{Devour God's Servants}  \index[scripture]{Psalms!Psa 079:07}(Psa 79:7)
    \item They cause \textbf{Doubt of the Savior}  \index[scripture]{Psalms!Psa 079:10}(Psa 79:10)
    \item They have a \textbf{Destiny that is Certain}  \index[scripture]{Psalms!Psa 079:12}(Psa 79:12)
\end{compactenum}}






%\footnote{\textcolor[rgb]{0.00,0.25,0.00}{\hyperlink{PsalmsTOC}{Return to end of Table of Contents.}}}
\textcolor[cmyk]{0.99998,1,0,0}{A Psalm of Asaph.}\\
\\
\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/psalms_79.html}{\textcolor[cmyk]{0.99998,1,0,0}{Psalm 79 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{O God, the heathen are come into thine inheritance; thy holy temple have they \fcolorbox{bone}{lime}{defiled}; they have laid Jerusalem on heaps.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{The \fcolorbox{bone}{lime}{dead} bodies of thy servants have they given \emph{to} \emph{be} meat unto the fowls of the heaven, the flesh of thy saints unto the beasts of the earth.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{Their blood have they shed like water round about Jerusalem; and \emph{there} \emph{was} none to bury \emph{them}.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{We are become a reproach to our neighbours, a \fcolorbox{bone}{lime}{scorn and derision} to them that are round about us.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{How long, LORD? wilt thou be angry for ever? shall thy jealousy burn like fire?}
[6] \textcolor[cmyk]{0.99998,1,0,0}{Pour out thy wrath upon the heathen that have not known thee, and upon the kingdoms that have not called upon thy name.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{For they have \fcolorbox{bone}{lime}{devoured} Jacob, and laid waste his \fcolorbox{bone}{lime}{dwelling} place.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{O remember not against us former iniquities: let thy tender mercies speedily prevent us: for we are brought very low.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{Help us, O God of our salvation, for the glory of thy name: and deliver us, and purge away our sins, for thy name's sake.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{Wherefore should the heathen say, \fcolorbox{bone}{lime}{Where \emph{is}} their God? let him be known among the heathen in our sight \emph{by} the revenging of the blood of thy servants \emph{which} \emph{is} shed.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{Let the sighing of the prisoner come before thee; according to the greatness of thy power preserve thou those that are appointed to die;}
[12] \textcolor[cmyk]{0.99998,1,0,0}{And render unto our neighbours sevenfold into their bosom their \fcolorbox{bone}{lime}{reproach}, wherewith they have reproached thee, O Lord.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{So we thy people and sheep of thy pasture will give thee thanks for ever: we will shew forth thy praise to all generations.}