\chapter{Judges 21}


\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{AN EVEN WORSE ENDING}}\\ (Judges 21:1-25) \begin{compactenum}[I.][8]
    \item The \textbf{Hasty Vow}   \index[scripture]{Judges!Jdg 21:01}(Jdg 21:1)
    \item \textbf{Heartfelt Voices}   \index[scripture]{Judges!Jdg 21:02}(Jdg 21:2)
    \item A \textbf{Hard Verdict}   \index[scripture]{Judges!Jdg 21:05}(Jdg 21:5)
    \item \textbf{Hired Valient}   \index[scripture]{Judges!Jdg 21:10}(Jdg 21:10)
    \item Four \textbf{Hundred Virgins}   \index[scripture]{Judges!Jdg 21:12}(Jdg 21:12)
    \item \textbf{Hidden in the Vineyards}   \index[scripture]{Judges!Jdg 21:21}(Jdg 21:21)
    \item A \textbf{Headship Void}   \index[scripture]{Judges!Jdg 21:25}(Jdg 21:25)
\end{compactenum}}





\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/judges_21.html}{\textcolor[cmyk]{0.99998,1,0,0}{Judges 21 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{Now the men of Israel had \fcolorbox{bone}{lime}{sworn} in Mizpeh, saying, There shall not any of us give his daughter unto Benjamin to wife.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And the people came to the house of God, and abode there till even before God, and lifted up their \fcolorbox{bone}{lime}{voices}, and wept sore;}
[3] \textcolor[cmyk]{0.99998,1,0,0}{And said, O LORD God of Israel, why is this come to pass in Israel, that there should be to day one tribe lacking in Israel?}
[4] \textcolor[cmyk]{0.99998,1,0,0}{And it came to pass on the morrow, that the people rose early, and built there an altar, and offered burnt offerings and peace offerings.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{And the children of Israel said, Who \emph{is} \emph{there} among all the tribes of Israel that came not up with the congregation unto the LORD? For \fcolorbox{bone}{bone}{they} had made a great oath concerning him that came not up to the LORD to Mizpeh, saying, He shall surely be \fcolorbox{bone}{lime}{put to death}.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{And the children of Israel repented them for Benjamin their brother, and said, There is one tribe cut off from Israel this day.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{How shall we do for wives for them that remain, seeing we have sworn by the LORD that we will not give them of our daughters to wives?}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{they} said, What one \emph{is} \emph{there} of the tribes of Israel that came not up to Mizpeh to the LORD? And, behold, there came none to the camp from Jabesh-gilead to the assembly.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{For the people were numbered, and, behold, \emph{there} \emph{were} none of the inhabitants of Jabesh-gilead there.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{And the congregation sent thither twelve thousand men of the \fcolorbox{bone}{lime}{valiantest}, and commanded them, saying, Go and smite the inhabitants of Jabesh-gilead with the edge of the sword, with the women and the children.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{And this \emph{is} the thing that ye shall do, Ye shall utterly destroy every male, and every woman that hath lain by man.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{they} found among the inhabitants of Jabesh-gilead four hundred young \fcolorbox{bone}{lime}{virgins}, that had known no man by lying with any male: and \fcolorbox{bone}{bone}{they} brought them unto the camp to Shiloh, which \emph{is} in the land of Canaan.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{And the whole congregation sent \emph{some} to speak to the children of Benjamin that \emph{were} in the rock Rimmon, and to call peaceably unto them.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{And Benjamin came again at that time; and \fcolorbox{bone}{bone}{they} gave them wives which \fcolorbox{bone}{bone}{they} had saved alive of the women of Jabesh-gilead: and yet so \fcolorbox{bone}{bone}{they} sufficed them not.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{And the people repented them for Benjamin, because that the LORD had made a breach in the tribes of Israel.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Then the elders of the congregation said, How shall we do for wives for them that remain, seeing the women are destroyed out of Benjamin?}
[17] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{they} said, \emph{There} \emph{must} \emph{be} an inheritance for them that be escaped of Benjamin, that a tribe be not destroyed out of Israel.}
[18] \textcolor[cmyk]{0.99998,1,0,0}{Howbeit we may not give them wives of our daughters: for the children of Israel have sworn, saying, Cursed \emph{be} he that giveth a wife to Benjamin.}
[19] \textcolor[cmyk]{0.99998,1,0,0}{Then \fcolorbox{bone}{bone}{they} said, Behold, \emph{there} \emph{is} a feast of the LORD in Shiloh yearly \emph{in} \emph{a} \emph{place} which \emph{is} on the north side of Beth-el, on the east side of the highway that goeth up from Beth-el to Shechem, and on the south of Lebonah.}
[20] \textcolor[cmyk]{0.99998,1,0,0}{Therefore \fcolorbox{bone}{bone}{they} commanded the children of Benjamin, saying, Go and lie in wait in the vineyards;}
[21] \textcolor[cmyk]{0.99998,1,0,0}{And see, and, behold, if the daughters of Shiloh come out to dance in dances, then come ye out of the \fcolorbox{bone}{lime}{vineyards}, and catch you every man his wife of the daughters of Shiloh, and go to the land of Benjamin.}
[22] \textcolor[cmyk]{0.99998,1,0,0}{And it shall be, when their fathers or their brethren come unto us to complain, that we will say unto them, Be favourable unto them for our sakes: because we reserved not to each man his wife in the war: for ye did not give unto them at this time, \emph{that} ye should be guilty.}
[23] \textcolor[cmyk]{0.99998,1,0,0}{And the children of Benjamin did so, and took \emph{them} wives, according to their number, of them that danced, whom \fcolorbox{bone}{bone}{they} caught: and \fcolorbox{bone}{bone}{they} went and returned unto their inheritance, and repaired the cities, and dwelt in them.}
[24] \textcolor[cmyk]{0.99998,1,0,0}{And the children of Israel departed thence at that time, every man to his tribe and to his family, and \fcolorbox{bone}{bone}{they} went out from thence every man to his inheritance.}
[25] \textcolor[cmyk]{0.99998,1,0,0}{In those days \emph{there} \emph{was} \fcolorbox{bone}{lime}{no king} in Israel: every man did \emph{that} \emph{which} \emph{was} right in his own eyes.}
