\chapter{Judges 20}


\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{ISRAEL'S FIRST CIVIL WAR}}\\ (Judges 20:1-48) \begin{compactenum}[I.][8]
    \item The \textbf{Consequences} of moral relativism% \index[scripture]{Judges!Judges 19:02}(Judges 19:2)
    \item A \textbf{Culture} Gone bad \index[scripture]{Judges!Jdg 20:01}(Jdg 20:1)
    \item A \textbf{Congregation} gathered \index[scripture]{Judges!Jdg 20:01}(Jdg 20:1)
    \item The \textbf{Concern} over Evil \index[scripture]{Judges!Jdg 20:08}(Jdg 20:8)
    \item An \textbf{Encampment}  \index[scripture]{Judges!Jdg 20:19}(Jdg 20:19)
    \item The \textbf{Count}  \index[scripture]{Judges!Jdg 20:46}(Jdg 20:46)
    \item The \textbf{Conflagrations}  \index[scripture]{Judges!Jdg 20:48}(Jdg 20:48)
\end{compactenum}}





\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/judges_20.html}{\textcolor[cmyk]{0.99998,1,0,0}{Judges 20 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{Then all the children of Israel went out, and the congregation was \fcolorbox{bone}{lime}{gathered} together as one man, from Dan even to Beer-sheba, with the land of Gilead, unto the LORD in Mizpeh.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And the chief of all the people, \emph{even} of all the tribes of Israel, presented themselves in the assembly of the people of God, four hundred thousand footmen that drew sword.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{(Now the children of Benjamin heard that the children of Israel were gone up to Mizpeh.) Then said the children of Israel, Tell \emph{us}, how was this wickedness?}
[4] \textcolor[cmyk]{0.99998,1,0,0}{And the Levite, the husband of the woman that was slain, answered and said, I came into Gibeah that \emph{belongeth} to Benjamin, I and my concubine, to lodge.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{And the men of Gibeah rose against me, and beset the house round about upon me by night, \emph{and} thought to have slain me: and my concubine have they forced, that she is dead.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{And I took my concubine, and cut her in pieces, and sent her throughout all the country of the inheritance of Israel: for they have committed lewdness and folly in Israel.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{Behold, ye \emph{are} all children of Israel; give here your advice and counsel.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And all the people arose as one man, saying, We will not any \emph{of} \emph{us} \fcolorbox{bone}{lime}{go to his tent}, neither will we any \emph{of} \emph{us} turn into his house.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{But now this \emph{shall} \emph{be} the thing which we will do to Gibeah; \emph{we} \emph{will} \emph{go} \emph{up} by lot against it;}
[10] \textcolor[cmyk]{0.99998,1,0,0}{And we will take ten men of an hundred throughout all the tribes of Israel, and an hundred of a thousand, and a thousand out of ten thousand, to fetch victual for the people, that they may do, when they come to Gibeah of Benjamin, according to all the folly that they have wrought in Israel.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{So all \fcolorbox{bone}{bone}{the men of Israel} were gathered against the city, knit together as one man.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And the tribes of Israel sent men through all the tribe of Benjamin, saying, What wickedness \emph{is} this that is done among you?}
[13] \textcolor[cmyk]{0.99998,1,0,0}{Now therefore deliver \emph{us} the men, the children of Belial, which \emph{are} in Gibeah, that we may put them to death, and put away evil from Israel. But the children of Benjamin would not hearken to the voice of their brethren the children of Israel:}
[14] \textcolor[cmyk]{0.99998,1,0,0}{But the children of Benjamin gathered themselves together out of the cities unto Gibeah, to go out to battle against the children of Israel.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{And the children of Benjamin were numbered at that time out of the cities twenty and six thousand men that drew sword, beside the inhabitants of Gibeah, which were numbered seven hundred chosen men.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{Among all this people \emph{there} \emph{were} seven hundred chosen men lefthanded; every one could sling stones at an hair \emph{breadth}, and not miss.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{the men of Israel}, beside Benjamin, were numbered four hundred thousand men that drew sword: all these \emph{were} men of war.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And the children of Israel arose, and went up to the house of God, and asked counsel of God, and said, Which of us shall go up first to the battle against the children of Benjamin? And the LORD said, Judah \emph{shall} \emph{go} \emph{up} first.}
[19] \textcolor[cmyk]{0.99998,1,0,0}{And the children of Israel rose up in the morning, and \fcolorbox{bone}{lime}{encamped} against Gibeah.}
[20] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{the men of Israel} went out to battle against Benjamin; and \fcolorbox{bone}{bone}{the men of Israel} put themselves in array to fight against them at Gibeah.}
[21] \textcolor[cmyk]{0.99998,1,0,0}{And the children of Benjamin came forth out of Gibeah, and destroyed down to the ground of the Israelites that day twenty and two thousand men.}
[22] \textcolor[cmyk]{0.99998,1,0,0}{And the people \fcolorbox{bone}{bone}{the men of Israel} encouraged themselves, and set their battle again in array in the place where they put themselves in array the first day.}
[23] \textcolor[cmyk]{0.99998,1,0,0}{(And the children of Israel went up and wept before the LORD until even, and asked counsel of the LORD, saying, Shall I go up again to battle against the children of Benjamin my brother? And the LORD said, Go up against him.)}
[24] \textcolor[cmyk]{0.99998,1,0,0}{And the children of Israel came near against the children of Benjamin the second day.}
[25] \textcolor[cmyk]{0.99998,1,0,0}{And Benjamin went forth against them out of Gibeah the second day, and destroyed down to the ground of the children of Israel again eighteen thousand men; all these drew the sword.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Then all the children of Israel, and all the people, went up, and came unto the house of God, and wept, and sat there before the LORD, and fasted that day until even, and offered burnt offerings and peace offerings before the LORD.}
[27] \textcolor[cmyk]{0.99998,1,0,0}{And the children of Israel enquired of the LORD, (for the ark of the covenant of God \emph{was} there in those days,}
[28] \textcolor[cmyk]{0.99998,1,0,0}{And Phinehas, the son of Eleazar, the son of Aaron, stood before it in those days,) saying, Shall I yet again go out to battle against the children of Benjamin my brother, or shall I cease? And the LORD said, Go up; for to morrow I will deliver them into thine hand.}
[29] \textcolor[cmyk]{0.99998,1,0,0}{And Israel set liers in wait round about Gibeah.}
[30] \textcolor[cmyk]{0.99998,1,0,0}{And the children of Israel went up against the children of Benjamin on the third day, and put themselves in array against Gibeah, as at other times.}
[31] \textcolor[cmyk]{0.99998,1,0,0}{And the children of Benjamin went out against the people, \emph{and} were drawn away from the city; and they began to smite of the people, \emph{and} kill, as at other times, in the highways, of which one goeth up to the house of God, and the other to Gibeah in the field, about thirty men of Israel.}
[32] \textcolor[cmyk]{0.99998,1,0,0}{And the children of Benjamin said, They \emph{are} smitten down before us, as at the first. But the children of Israel said, Let us flee, and draw them from the city unto the highways.}
[33] \textcolor[cmyk]{0.99998,1,0,0}{And all \fcolorbox{bone}{bone}{the men of Israel} rose up out of their place, and put themselves in array at Baal-tamar: and the liers in wait of Israel came forth out of their places, \emph{even} out of the meadows of Gibeah.}
[34] \textcolor[cmyk]{0.99998,1,0,0}{And there came against Gibeah ten thousand chosen men out of all Israel, and the battle was sore: but they knew not that evil \emph{was} near them.}
[35] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD smote Benjamin before Israel: and the children of Israel destroyed of the Benjamites that day twenty and five thousand and an hundred men: all these drew the sword.}
[36] \textcolor[cmyk]{0.99998,1,0,0}{So the children of Benjamin saw that they were smitten: for \fcolorbox{bone}{bone}{the men of Israel} gave place to the Benjamites, because they trusted unto the liers in wait which they had set beside Gibeah.}
[37] \textcolor[cmyk]{0.99998,1,0,0}{And the liers in wait hasted, and rushed upon Gibeah; and the liers in wait drew \emph{themselves} along, and smote all the city with the edge of the sword.}
[38] \textcolor[cmyk]{0.99998,1,0,0}{Now there was an appointed sign between \fcolorbox{bone}{bone}{the men of Israel} and the liers in wait, that they should make a great flame with smoke rise up out of the city.}
[39] \textcolor[cmyk]{0.99998,1,0,0}{And when \fcolorbox{bone}{bone}{the men of Israel} retired in the battle, Benjamin began to smite \emph{and} kill of \fcolorbox{bone}{bone}{the men of Israel} about thirty persons: for they said, Surely they are smitten down before us, as \emph{in} the first battle.}
[40] \textcolor[cmyk]{0.99998,1,0,0}{But when the flame began to arise up out of the city with a pillar of smoke, the Benjamites looked behind them, and, behold, the flame of the city ascended up to heaven.}
[41] \textcolor[cmyk]{0.99998,1,0,0}{And when \fcolorbox{bone}{bone}{the men of Israel} turned again, the men of Benjamin were amazed: for they saw that evil was come upon them.}
[42] \textcolor[cmyk]{0.99998,1,0,0}{Therefore they turned \emph{their} \emph{backs} before \fcolorbox{bone}{bone}{the men of Israel} unto the way of the wilderness; but the battle overtook them; and them which \emph{came} out of the cities they destroyed in the midst of them.}
[43] \textcolor[cmyk]{0.99998,1,0,0}{\emph{Thus} they inclosed the Benjamites round about, \emph{and} chased them, \emph{and} trode them down with ease over against Gibeah toward the sunrising.}
[44] \textcolor[cmyk]{0.99998,1,0,0}{And there fell of Benjamin eighteen thousand men; all these \emph{were} men of valour.}
[45] \textcolor[cmyk]{0.99998,1,0,0}{And they turned and fled toward the wilderness unto the rock of Rimmon: and they gleaned of them in the highways five thousand men; and pursued hard after them unto Gidom, and slew two thousand men of them.}
[46] \textcolor[cmyk]{0.99998,1,0,0}{So that all which fell that day of Benjamin were \fcolorbox{bone}{lime}{twenty and five thousand} men that drew the sword; all these \emph{were} men of valour.}
[47] \textcolor[cmyk]{0.99998,1,0,0}{But six hundred men turned and fled to the wilderness unto the rock Rimmon, and abode in the rock Rimmon four months.}
[48] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{the men of Israel} turned again upon the children of Benjamin, and smote them with the edge of the sword, as well the men of \emph{every} city, as the beast, and all that came to hand: also they set on fire all the cities that they came to.}