\chapter{Judges 19}
\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{DARK DAYS IN ISRAEL}}\\ (Judges 19:1-30) \begin{compactenum}[I.][8]
    \item \textbf{Playing} the Harlot \index[scripture]{Judges!Jdg 19:02}(Jdg 19:2)
    \item \textbf{Problem}  Resolved  \index[scripture]{Judges!Jdg 19:10}(Jdg 19:10)
    \item \textbf{Provision}   \index[scripture]{Judges!Jdg 19:19}(Jdg 19:19)
    \item \textbf{Perversion}  Unrestrained \index[scripture]{Judges!Jdg 19:22}(Jdg 19:22)
    \item Gang \textbf{Rape}  \index[scripture]{Judges!Jdg 19:25}(Jdg 19:25)
    \item \textbf{Pieces}  Sent \index[scripture]{Judges!Jdg 19:29}(Jdg 19:29)
\end{compactenum}}





\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/judges_19.html}{\textcolor[cmyk]{0.99998,1,0,0}{Judges 19 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{And it came to pass in those days, when \emph{there} \emph{was} no king in Israel, that there was a certain Levite sojourning on the side of mount Ephraim, who took to him a concubine out of Beth-lehem-judah.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And his concubine \fcolorbox{bone}{lime}{played the whore} against him, and went away from him unto her father's house to Beth-lehem-judah, and was there four whole months.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{And her husband arose, and went after her, to speak friendly unto her, \emph{and} to bring her again, having his servant with him, and a couple of asses: and she brought him into her father's house: and when the father of the damsel saw him, he rejoiced to meet him.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{And his father in law, the damsel's father, retained him; and he abode with him three days: so they did eat and drink, and lodged there.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And it came to pass on the fourth day, when they arose early in the morning, that he rose up to depart: and the damsel's father  \fcolorbox{bone}{bone}{said} unto his son in law, Comfort thine heart with a morsel of bread, and afterward go your way.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{And they sat down, and did eat and drink both of them together: for the damsel's father had  \fcolorbox{bone}{bone}{said} unto the man, Be content, I pray thee, and tarry all night, and let thine heart be merry.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{And when the man rose up to depart, his father in law urged him: therefore he lodged there again.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{And he arose early in the morning on the fifth day to depart: and the damsel's father  \fcolorbox{bone}{bone}{said}, Comfort thine heart, I pray thee. And they tarried until afternoon, and they did eat both of them.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{And when the man rose up to depart, he, and his concubine, and his servant, his father in law, the damsel's father,  \fcolorbox{bone}{bone}{said} unto him, Behold, now the day draweth toward evening, I pray you tarry all night: behold, the day groweth to an end, lodge here, that thine heart may be merry; and to morrow get you early on your way, that thou mayest go home.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{But the man would not tarry that night, but he rose up and \fcolorbox{bone}{lime}{departed}, and came over against Jebus, which \emph{is} Jerusalem; and \emph{there} \emph{were} with him two asses saddled, his concubine also \emph{was} with him.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{\emph{And} when they \emph{were} by Jebus, the day was far spent; and the servant  \fcolorbox{bone}{bone}{said} unto his master, Come, I pray thee, and let us turn in into this city of the Jebusites, and lodge in it.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{And his master  \fcolorbox{bone}{bone}{said} unto him, We will not turn aside hither into the city of a stranger, that \emph{is} not of the children of Israel; we will pass over to Gibeah.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{And he  \fcolorbox{bone}{bone}{said} unto his servant, Come, and let us draw near to one of these places to lodge all night, in Gibeah, or in Ramah.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{And they passed on and went their way; and the sun went down upon them \emph{when} \emph{they} \emph{were} by Gibeah, which \emph{belongeth} to Benjamin.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{And they turned aside thither, to go in \emph{and} to lodge in Gibeah: and when he went in, he sat him down in a street of the city: for \emph{there} \emph{was} no man that took them into his house to lodging.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And, behold, there came an old man from his work out of the field at even, which \emph{was} also of mount Ephraim; and he sojourned in Gibeah: but the men of the place \emph{were} Benjamites.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{And when he had lifted up his eyes, he saw a wayfaring man in the street of the city: and the old man  \fcolorbox{bone}{bone}{said}, Whither goest thou? and whence comest thou?}
[18] \textcolor[cmyk]{0.99998,1,0,0}{And he  \fcolorbox{bone}{bone}{said} unto him, We \emph{are} passing from Beth-lehem-judah toward the side of mount Ephraim; from thence \emph{am} I: and I went to Beth-lehem-judah, but I \emph{am} \emph{now} going to the house of the LORD; and there \emph{is} no man that receiveth me to house.}
[19] \textcolor[cmyk]{0.99998,1,0,0}{Yet there is both straw and \fcolorbox{bone}{lime}{provender} for our asses; and there is bread and wine also for me, and for thy handmaid, and for the young man \emph{which} \emph{is} with thy servants: \emph{there} \emph{is} no want of any thing.}
[20] \textcolor[cmyk]{0.99998,1,0,0}{And the old man  \fcolorbox{bone}{bone}{said}, Peace \emph{be} with thee; howsoever \emph{let} all thy wants \emph{lie} upon me; only lodge not in the street.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{So he brought him into his house, and gave provender unto the asses: and they washed their feet, and did eat and drink.}
[22] \textcolor[cmyk]{0.99998,1,0,0}{\emph{Now} as they were making their hearts merry, behold, the men of the city, certain sons of Belial, beset the house round about, \emph{and} beat at the door, and spake to the master of the house, the old man, saying, Bring forth the man that came into thine house, \fcolorbox{bone}{lime}{that we may know him}.}
[23] \textcolor[cmyk]{0.99998,1,0,0}{And the man, the master of the house, went out unto them, and  \fcolorbox{bone}{bone}{said} unto them, Nay, my brethren, \emph{nay}, I pray you, do not \emph{so} wickedly; seeing that this man is come into mine house, do not this folly.}
[24] \textcolor[cmyk]{0.99998,1,0,0}{Behold, \emph{here} \emph{is} my daughter a maiden, and his concubine; them I will bring out now, and humble ye them, and do with them what seemeth good unto you: but unto this man do not so vile a thing.}
[25] \textcolor[cmyk]{0.99998,1,0,0}{But the men would not hearken to him: so the man took his concubine, and brought her forth unto them; and \fcolorbox{bone}{lime}{they knew her}, and abused her all the night until the morning: and when the day began to spring, they let her go.}
[26] \textcolor[cmyk]{0.99998,1,0,0}{Then came the woman in the dawning of the day, and fell down at the door of the man's house where her lord \emph{was}, till it was light.}
[27] \textcolor[cmyk]{0.99998,1,0,0}{And her lord rose up in the morning, and opened the doors of the house, and went out to go his way: and, behold, the woman his concubine was fallen down \emph{at} the door of the house, and her hands \emph{were} upon the threshold.}
[28] \textcolor[cmyk]{0.99998,1,0,0}{And he  \fcolorbox{bone}{bone}{said} unto her, Up, and let us be going. But none answered. Then the man took her \emph{up} upon an ass, and the man rose up, and gat him unto his place.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And when he was come into his house, he took a knife, and laid hold on his concubine, and divided her, \emph{together} with her bones, into twelve \fcolorbox{bone}{lime}{pieces}, and sent her into all the coasts of Israel.}
[30] \textcolor[cmyk]{0.99998,1,0,0}{And it was so, that all that saw it  \fcolorbox{bone}{bone}{said}, There was no such deed done nor seen from the day that the children of Israel came up out of the land of Egypt unto this day: consider of it, take advice, and speak \emph{your} \emph{minds}.}
