\chapter{Ruth 3}





\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{FINDING A HUSBAND}}\\ (Ruth 3:1-18) \begin{compactenum}[I.][8]
    \item  \textbf{Rest}  \index[scripture]{Ruth!Ruth 03:01}(Ruth 3:1)
    \item The \textbf{Request} with Grace \index[scripture]{Ruth!Ruth 03:06--09}(Ruth 3:6--9)
    \item The \textbf{Reassurance} with Grace \index[scripture]{Ruth!Ruth 03:10--18--09}(Ruth 3:10--18)
    \item  The \textbf{Redeemer}  \index[scripture]{Ruth!Ruth 03:11}(Ruth 3:11)
    \item  The \textbf{Reputation}  \index[scripture]{Ruth!Ruth 03:11}(Ruth 3:11)
    \item  The \textbf{Relative}  \index[scripture]{Ruth!Ruth 03:12}(Ruth 3:12)
    \item  The \textbf{Rush}  \index[scripture]{Ruth!Ruth 03:17}(Ruth 3:17)
\end{compactenum}}







\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/ruth_3.html}{\textcolor[cmyk]{0.99998,1,0,0}{Ruth 3 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{Then Naomi her mother in law said unto her, My daughter, shall I not seek \fcolorbox{bone}{lime}{rest} for thee, that it may be well with thee?}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And now \emph{is} not Boaz of our kindred, with whose maidens thou wast? Behold, he winnoweth barley to night in the threshingfloor.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{Wash thyself therefore, and anoint thee, and put thy raiment upon thee, and get thee down to the floor: \emph{but} make not thyself known unto the man, until he shall have done eating and drinking.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{And it shall be, when he lieth down, that thou shalt mark the place where he shall lie, and thou shalt go in, and uncover his feet, and lay thee down; and he will tell thee what thou shalt do.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{she} said unto her, All that thou sayest unto me I will do.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{she} went down unto the floor, and did according to all that her mother in law bade her.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{And when Boaz had eaten and drunk, and his heart was merry, he went to lie down at the end of the heap of corn: and \fcolorbox{bone}{bone}{she} came softly, and \fcolorbox{bone}{lime}{uncovered his feet}, and laid her down.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And it came to pass at midnight, that the man was afraid, and turned himself: and, behold, a woman lay at his feet.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{And he said, Who \emph{art} thou? And \fcolorbox{bone}{bone}{she} answered, I \emph{am} Ruth thine handmaid: spread therefore thy skirt over thine handmaid; for thou \emph{art} a near kinsman.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{And he said, \fcolorbox{bone}{lime}{Blessed \emph{be} thou} of the LORD, my daughter: \emph{for} thou hast shewed more kindness in the latter end than at the beginning, inasmuch as thou followedst not young men, whether poor or rich.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{And now, my daughter, fear not; I will do to thee all that thou \fcolorbox{bone}{lime}{requirest}: for all the city of my people doth know that thou \emph{art} a \fcolorbox{bone}{lime}{virtuous} woman.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{And now it is true that I \emph{am} \emph{thy} near kinsman: howbeit there is a kinsman nearer than I.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{Tarry this night, and it shall be in the morning, \emph{that} if he will perform unto thee the part of a \fcolorbox{bone}{lime}{kinsman}, well; let him do the kinsman's part: but if he will not do the part of a kinsman to thee, then will I do the part of a kinsman to thee, \emph{as} the LORD liveth: lie down until the morning.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{she} lay at his feet until the morning: and \fcolorbox{bone}{bone}{she} rose up before one could know another. And he said, Let it not be known that a woman came into the floor.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{Also he said, Bring the vail that \emph{thou} \emph{hast} upon thee, and hold it. And when \fcolorbox{bone}{bone}{she} held it, he measured six \emph{measures} of barley, and laid \emph{it} on her: and \fcolorbox{bone}{bone}{she} went into the city.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{And when \fcolorbox{bone}{bone}{she} came to her mother in law, \fcolorbox{bone}{bone}{she} said, Who \emph{art} thou, my daughter? And \fcolorbox{bone}{bone}{she} told her all that the man had done to her.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{she} said, These six \emph{measures} of barley gave he me; for he said to me, \fcolorbox{bone}{lime}{Go not empty} unto thy mother in law.}
[18] \textcolor[cmyk]{0.99998,1,0,0}{Then said \fcolorbox{bone}{bone}{she}, Sit still, my daughter, until thou know how the matter will fall: for the man will not be in rest, until he have finished the thing this day.}