\chapter{Ruth 1}


\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{COMING BACK BROKEN}}\\ (Ruth 1:1-22) \begin{compactenum}[I.][8]
    \item The \textbf{Longing} (for Food) \index[scripture]{Ruth!Ruth 01:01}(Ruth 1:1)
    \item The \textbf{Looking} (at Moab) \index[scripture]{Ruth!Ruth 01:01}(Ruth 1:1)
    \item The \textbf{Leaving} (the land of faith for the land of the flesh) \index[scripture]{Ruth!Ruth 01:01}(Ruth 1:1)
    \item The \textbf{Loosing} (husband and sons) \index[scripture]{Ruth!Ruth 01:03}\index[scripture]{Ruth!Ruth 01:05}(Ruth 1:3, 5)
    \item The \textbf{Learning} (why did she have to suffer loss to know she was in the wrong place?) 
    \item The \textbf{Listening} (why was this a surprise to her?)  \index[scripture]{Ruth!Ruth 01:06}(Ruth 1:6)
    \item Ruth's \textbf{Oblivion} (Naomi was oblivious to Ruth's faith)  %\index[scripture]{Ruth!Ruth 01:06}(Ruth 1:6)
\end{compactenum}}




\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/ruth_1.html}{\textcolor[cmyk]{0.99998,1,0,0}{Ruth 1 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{Now it came to pass in the days when the judges ruled, that there was a \fcolorbox{bone}{lime}{famine} in the land. And a certain man of Beth-lehem-judah \fcolorbox{bone}{lime}{went} to sojourn in the country of Moab, he, and his wife, and his two sons.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And the name of the man \emph{was} Elimelech, and the name of his wife Naomi, and the name of his two sons Mahlon and Chilion, Ephrathites of Beth-lehem-judah. And they came into the country of Moab, and continued there.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{And Elimelech Naomi's \fcolorbox{bone}{lime}{husband died}; and she was left, and her two sons.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{And they took them wives of the women of Moab; the name of the one \emph{was} Orpah, and the name of the other Ruth: and they dwelled there about ten years.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{lime}{Mahlon and Chilion} died also both of them; and the woman was left of her two sons and her husband.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Then she arose with her daughters in law, that she might return from the country of Moab: for she had \fcolorbox{bone}{lime}{heard} in the country of Moab how that the LORD had visited his people in giving them bread.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{Wherefore she went forth out of the place where she was, and her two daughters in law with her; and they went on the way to return unto the land of Judah.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{And Naomi said unto her two daughters in law, Go, return each to her mother's house: the LORD deal kindly with you, as ye have dealt with the dead, and with me.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{The LORD grant you that ye may find rest, each \emph{of} \emph{you} in the house of her husband. Then she kissed them; and they lifted up their voice, and wept.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{And they said unto her, Surely we will return with thee unto thy people.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{And Naomi said, Turn again, my daughters: why will ye go with me? \emph{are} there yet \emph{any} \emph{more} sons in my womb, that they may be your husbands?}
[12] \textcolor[cmyk]{0.99998,1,0,0}{Turn again, my daughters, go \emph{your} \emph{way}; for I am too old to have an husband. If I should say, I have hope, \emph{if} I should have an husband also to night, and should also bear sons;}
[13] \textcolor[cmyk]{0.99998,1,0,0}{Would ye tarry for them till they were grown? would ye stay for them from having husbands? nay, my daughters; for it grieveth me much for your sakes that the hand of the LORD is gone out against me.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{And they lifted up their voice, and wept again: and Orpah kissed her mother in law; but Ruth clave unto her.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{And she said, Behold, thy sister in law is gone back unto her people, and unto her gods: return thou after thy sister in law.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{And Ruth said, Intreat me not to leave thee, \emph{or} to return from following after thee: for whither thou goest, I will go; and where thou lodgest, I will lodge: thy people \emph{shall} \emph{be} my people, and thy God my God:}
[17] \textcolor[cmyk]{0.99998,1,0,0}{Where thou diest, will I die, and there will I be buried: the LORD do so to me, and more also, \emph{if} \emph{ought} but death part thee and me.}
[18] \textcolor[cmyk]{0.99998,1,0,0}{When she saw that she was stedfastly minded to go with her, then she left speaking unto her.}
[19] \textcolor[cmyk]{0.99998,1,0,0}{So they two went until they came to Beth-lehem. And it came to pass, when they were come to Beth-lehem, that all the city was moved about them, and they said, \emph{Is} this Naomi?}
[20] \textcolor[cmyk]{0.99998,1,0,0}{And she said unto them, Call me not Naomi, call me Mara: for the Almighty hath dealt very bitterly with me.}
[21] \textcolor[cmyk]{0.99998,1,0,0}{I went out full, and the LORD hath brought me home again empty: why \emph{then} call ye me Naomi, seeing the LORD hath testified against me, and the Almighty hath afflicted me?}
[22] \textcolor[cmyk]{0.99998,1,0,0}{So Naomi returned, and Ruth the Moabitess, her daughter in law, with her, which returned out of the country of Moab: and they came to Beth-lehem in the beginning of barley harvest.}
